Talks

### 2024-11-20 talks.qmd
update

@@

>>>>

- 20 November: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1yuXXm398di67hA3NwgJf5pRZ39LVPWHg/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)

@@

- 23 October: (chair) AFIRE Funder's Forum - promoting experiments by research funders:  [slides](https://docs.google.com/presentation/d/19XrX5qCxNrBIfYrUIEd832eQ17nE6Ad5/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
